\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-26 paper.tex
evaluation-figs
2-approx speed up left

\begin{abstract}
Inter-DataCenter Wide Area Network (Inter-DC WAN) that connects geographically distributed data centers is becoming one of the most critical network infrastructures.
%Network failures are common in WANs, so the provision of high availability has been a major focus of network research.
Due to the limited bandwidth resources and inevitable link failures, it is highly challenging to guarantee network availability for services, especially those with stringent bandwidth demands, over inter-DC WAN.
%While modern datacenter services increasingly call for high availability, network failures in WANs remain a fairly common phenomenon.
%Most traffic engineering schemes only consider connectivity-based availability and this severely degrades quality of service, thus revenue.
We present $\mathsf{BATE}$,
a novel Traffic Engineering (TE)  framework that 
%contains admission control, online scheduling and failure recovery.
aims for \textit{bandwidth availability} (BA) provision, where a service level agreement (SLA) defines that a demand on certain bandwidth should be satisfied with a stipulated probability,  when subjected to the network capacity and possible failures of the inter-DC WAN.
%Also, $\mathsf{BATE}$ is able to maximize revenue when network fails.
%$\mathsf{BATE}$ tries to guarantee the bandwidth-based availability of demands . 
%$\mathsf{BATE}$ generates a probabilistic failure model from empirical data and maximizes the profit that can be achieved under certain constrains on  bandwidth-based availability. 
%For the failure model, we propose a pruning algorithm to reduce the problem size.
%For the optimization problem, we prove it is NP-hard and  propose a greedy algorithm to efficiently solve it with only minor profit loss. 
%We design and implement an SDN-based system named $\mathsf{Dionysus}$ to deploy $\mathsf{BATE}$ over inter-DC WAN.
The three core components of  $\mathsf{BATE}$, i.e., admission control, traffic scheduling and failure recovery, are built on different mathematical models and theoretically analyzed. 
They are also extensively compared against state-of-the-art TE schemes, using testbed as well as trace driven simulations across different topologies, traffic matrices and failure scenarios. 
Our evaluation demonstrates that, compared with the optimal admission strategy, $\mathsf{BATE}$ can speed up the online admission control by 30$\times$ at the expense of less than 4\% false rejections. 
On the other hand, compared with the latest TE schemes like FFC and TEAVAR,   $\mathsf{BATE}$ can meet the bandwidth availability SLAs for 40\% more demands, and when network failure causes SLA violations, it can retain 25\% more profit  under a simple pricing and refunding model.
%.
% $\mathsf{BATE}$ can 
%(1) achieve 30 $\times$ speedup in admission control time at the expense of sacrificing 8\% in performance compared to the optimal stragety;
%(2) increase the percentage of demands that satisfy their availability SLAs by up to 40\%;
%(3) hold 30\% more profit for the provider when network fails. 
%The evaluation results demonstrate that $\mathsf{BATE}$ can make 20\%, 25\%, 30\%, 40\% more flows satisfy their bandwidth-based availability demands  than TEAVAR, SMORE, SWAN and FFC, respectively.
\end{abstract}

@@

Thirdly, 
we implement $\mathsf{BATE}$ as a real system, including a centralized controller and multiple brokers (one for each DC),  together with end-host clients (see $\S$\ref{system}).
 We conduct extensive experiments using a small testbed as well as trace driven large scale simulations (see $\S$\ref{evaluation}).
We compare  $\mathsf{BATE}$ with state-of-the-art WAN TE schemes such as TEAVAR \cite{Teavar}, SMORE \cite{SMORE}, SWAN \cite{swan}, B4 \cite{B4} and FFC \cite{FFC}, across different topologies, traffic matrices and failure scenarios.
Our evaluation demonstrates that $\mathsf{BATE}$ can 
(1) speed up the online admission control by 30$\times $ at the expense of a false rejection ratio that is less than 4\%;
(2) meet the bandwidth availability SLAs for 40\% more demands;
(3) retain 25\% more profit when network failure causes SLA violations, under a simple pricing and refunding model. 
To our knowledge, $\mathsf{BATE}$ is the first to tackle bandwidth availability provision over inter-DC WAN, where heterogeneities of demands and link failures are systematically taken into account for profit maximization.  
 %At last, we show the related works (see $\S$\ref{relate}).
%Traditionally, links are heavily underutilized to achieve a more rigorous availability target. 
%However, in reality, the failure probability of a single link can even differ by three orders of magnitude.
%Therefore, some link failure can be negligible and it makes no sense to reduce the utilization of these links.
%With the link Under BATE, links can maintain high utilization.

@@

If for every $k$, $R_{dk}$ is larger than its demand (i.e., $R_{dk} \ge 1$), 
then there is no problem since the demanded availability is still satisfied. 
However, if any $R_{dk}$ falls below 1, then the corresponding SLA will be violated. 
For simplicity, here we assume a simple pricing and refunding model, 
where the charge for serving a user demand $d$ is $g_d$, and if the SLA is violated, 
a fraction $\mu_d$ of $g_d$ will be refunded. 
We use $r_d$ to denote the profit of demand $d$ with refunding, such that
%If it is between $\beta_j^{k}$ and $\beta_j^{k+1}$, then the profit is $\alpha_j^k$, where $1>\alpha_j^1>\alpha_j^2>...>\alpha_j^k$.
\begin{equation*}
r_d=
\begin{cases}
g_d &\text{if $R_{dk} \ge 1$ for every $k \in K$}\\
(1-\mu_{d})g_d &\text{Otherwise}
\end{cases}
\label{availability222}
\end{equation*}

@@

%We begin by describing the experimental framework ($\S$ \ref{setting}). 
%We show the performance of $\mathsf{BATE}$ through answering the following specific questions:
%compared with the latest TE schemes like FFC and TEAVAR, BATE can meet the availability SLAs of 40% more bandwidth demands, and when network failure causes SLA violations, it can retain 30% more profit under a simple pricing and refunding model.
(1) $\mathsf{BATE}$ consistently outperforms latests TE algorithms under various topologies, traffic matrices and failure scenarios. With $\mathsf{BATE}$, up to 40\% more bandwidth availability demands can be successfully fulfilled, and 30\% more profit can be retained when failures occur.

(2) $\mathsf{BATE}$ achieves a good tradeoff between efficiency and optimality. 
Compared with the optimal solutions, (i) our admission control algorithm can speed up the admission procedure by 30$\times$ at the expense of less than 4\% false rejections, 
(ii) our pruning-augmented scheduling algorithm runs xx$\times$ faster while wasting only 6\% total bandwidth and losing only 8\% overall availability, 
and (iii) our greedy failure recovery algorithm can reduce the reaction time by xx$\times$, 
where the profit loss is below 10\%.

@@

\subsection{Simulations}
\textbf{Simulation setup.} 
We also conduct simulations on four real network topologies, including B4 \cite{B4}, ATT \cite{Teavar}, IBM\cite{SMORE} and a national-level backbone. 
Table \ref{evaluation-topologies} shows the topology details
\footnote{For B4, ATT and IBM, we get their topologies, link capacities and traffic matrices from the authors of TEAVAR\cite{Teavar}, and for the national backbone, we conduct a direct measurement on it but hide its name due to anonymity requirement.}. 
Following the conclusion on WAN failures in literature studies\cite{Characterization, Teavar}, 
we simulate link failures according to a Weibull distribution with its shape $\lambda=0.8$ and scale $k=0.00001$. 
We generate the demand workload in a similar way to that in the testbed. 
The arrivals of BA demands follow a Poisson process, where the mean arrival rate varies from 1 to 5 in each time slot. 
The duration of each demand follows an exponential distribution, and the mean duration corresponds to 1000 time slots.
The required bandwidth in each user demand is randomly drawn from the traffic metrices (we have collected 200 matrices for each topology) with a proper scale down factor (we use 5), so that between each source-destination pair, multiple users can be served simultaneously. 
The required availability in each user demand is drawn from 10 different SLAs of Azure\cite{azure}.
In our simulations, besides FFC and TEAVAR, we also compare against several other TE algorithms,  
including SWAN \cite{swan}, SMORE \cite{SMORE} and B4 \cite{B4}. 
They have not explicitly considered availability, but pay attention to 
total throughput, link utilization or user fairness. 
These TE algorithms will be activated every 10 time slots.
We assume at most one link failure (i.e., no concurrent failures) in FFC,  
use 99.9\% (which is the maximum value in the user demands) as the default availability target in TEAVAR,
and let SWAN maximize the total throughput of all users. 
With the above settings, each simulation lasts 150,000 slots (corresponding to 100 days if each slot represents 1 minute), and the results achieved by each algorithm on each topology are calculated on 5 independent simulations with different workload traces. 
All the simulations are conducted on a Linux server with a quad-core 2.60GHz processor and 32GB memory.

@@

We then compare the traffic scheduling capability of $\mathsf{BATE}$ against FFC, TEAVAR, SWAN, SMORE and B4.
The methodology is similar to the post-processing simulation in TEAVAR \cite{Teavar}, 
where we simulate different failure scenarios according to their probabilities, 
and in each scenario we record the demands that can be satisfied. 
If the \textit{achieved availibility}, i.e., the total posterior probabilities of \textit{qualified} scenarios where a user's bandwidth target is met, is larger than the user's availability target, 
then the BA demand is \textit{satisfied}. 
We plot the overall percentage of satisfied BA demands under each arrival rate (averaged across all simulations) in Figure \ref{scheduling-benefit}(a). $\mathsf{BATE}$ nearly always achieves a satisfaction ratio around 100\%, with a leading margin of at least 20\% under a high arrival rate (rate=6 in the figure). 
To further demonstrates $\mathsf{BATE}$'s advantage in matching stringent availability requirements  
with reliable links, we further augment each TE algorithm with the \textit{fixed} admission control 
scheme. The satisfaction ratios are plotted in Figure \ref{scheduling-benefit}(b), where $\mathsf{BATE}$
still performs at least 10\% better than the others.

@@

Figure \ref{sim-profit} shows the average monetary gain percentage for the scenario in which one failure could occur in the network.
We can see $\mathsf{BATE}$  is able to retain 30\% more profit than other algorithms when network fails.

\begin{figure}
\centering
\subfigure[Cutoff error]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/error.pdf}}
\subfigure[Optimization time]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/optimization_time.pdf}}
\caption{Impact of pruning for traffic scheduling.}
\label{availability_fig3}
\end{figure}

@@

\begin{figure}[t]
   \begin{minipage}[t]{0.5\linewidth} 
    \centering 
    \includegraphics[width=1.6 in]{fig/evaluation/routing.pdf}
    \caption{Routings.} 
    \label{routing-version} 
  \end{minipage}% 
   \begin{minipage}[t]{0.5\linewidth} 
    \centering 
    \includegraphics[width=1.6 in]{fig/evaluation/approximation.pdf}
    \caption{Approximation.} 
    \label{approximation} 
  \end{minipage}

@@

Traffic scheduling algorithm cuts off the scenarios that can hardly happen.
%Algorithm \ref{pruning} runs in depth-first manner and when the current network state is smaller than the threshold, the remaining state of the search tree can be ignored.
%Figure \ref{purning_fig2} (a) shows the percentage of network state coverage.
%We can see that even with small cutoff threshold, more than 97\% probability are included.
% In Section \ref{solutions}, we show how to derive the solutions for WAPM problem.
% The errors mainly comes from two parts, i.e., ILP approximate algorithm and pruning.
%In Appendix \ref{B}, we analyze the approximation of the greedy heuristic is 2 in an ideal case.
%Algorithm \ref{greedy} proposes a greedy algorithm to solve $\mathsf{BATE}$ problem.
Let $\mathsf{BATE}$ denote the overall allocated bandwidth of all admitted demands with scenario pruning  and $OPT$ denote the allocated bandwidth of optimal solution without scenario pruning. 
Then the error can be defined as $\frac{|\mathsf{BATE} -OPT|}{|OPT|}$.
Figure \ref{availability_fig3} (a) shows the error of pruning algorithm with different current link failure numbers.
We can see the error is less than 8\% even the current link failure number is 1.
Traditionally, TE should update the network state every 5-10 minutes.
% and though the powerful mathematical optimization solver such as Gurobi \cite{gurobi} can solve $\mathsf{BATE}$ problem, it might be too slow.
Figure \ref{availability_fig3} (b) shows the time when solving it with Gurobi \cite{gurobi} on the server (4-core, 2.60GHz processor with 32GB ).
We can see that even on a large network (e.g., ATT topology), at most  15 seconds are needed when current link failure numbers are 2, which is fast enough in reality.
%We can see that for large network (e.g., ATT topology) , Gurobi is too slow to converge and the greedy algorithm is necessary.
%While the bruce force algorithm is more than 1000 minutes for each topology and we don't paint them in the picture.
%We can see the result is fast enough to deploy in practice.

So far, we use K-shortest path as the default tunnel selection scheme.
There are also other tunnel selection schemes, e.g., edge disjoint paths\cite{Bruno2013Dynamic}, oblivious routing\cite{SMORE}.
Figure \ref{routing-version} shows the comparison with different tunnel selection methods.
We can see that (1) $\mathsf{BATE}$ performs well regardless the tunnel selection algorithm.
This indicates that the success of $\mathsf{BATE}$ doesn't reply on the particular routing scheme;
(2)  Oblivious routing is still slighter better than KSP and edge disjoint paths.
This is because it is intended to avoid link over-utilization through diverse and low-stretch path selection.

We propose a greedy for failure recovery optimization problem.
Figure \ref{approximation} shows the approximation of the greedy algorithm, where the approximation can be defined as the profit ratio of optimal solution and greedy solution.
We can see that the profit loss of greedy algorithm is less than 10\%.
%Satisfaction percentage. It denotes the percentages of applications whose achieved availability is larger than the corresponding target.
%Figure \ref{availability_fig1}(b) shows 
%$\mathsf{BATE}$ performs about 20\%, 25\%, 30\%,  40\% better than TEAVAR, SMORE, SWAN, FFC, respectively.
%%Specially, when traffic scale is 3, more than 70\% applications can satisfy their availability demands, which is at least 30\% better than TEAVAR.
%Specially, the advantage of $\mathsf{BATE}$  is more obvious when there are resource competition (e.g., $s=3$).
%%The reason for this is that $\mathsf{BATE}$ considers the bandwidth-based availability demand differentiation of applications.
%This picture also demonstrates that the performance of $\mathsf{BATE}$ doesn't depend on particular network topology and traffic.
%Next, we take IBM trace as the example and perform the experiments.

@@

Use $a_d$ to represent whether the BA target of $d$ can be satisfied, which also means $a_d$ can be admitted, then we have 
\iffalse
\begin{equation}
 y_d=
\begin{cases}
1 &\text{$1 >S_d \ge \beta_{d}$}\\
0 &\text{$ \beta_{d} >S_d\ge 0 $}
\end{cases},
\ \ \ \forall  d \in D.
\label{availability4}
\end{equation}
\fi
\begin{equation*}
a_d=
\begin{cases}
1 &\text{if $ \beta_{d} \le s_d \le 1$}\\
0 &\text{if $ 0 \le s_d< \beta_{d} $}
\end{cases}
\label{availability4}
\end{equation*}
%If the achieved bandwidth  availability (i.e., $s_d$) is larger than its desired availability target (i.e., $\beta_d$), the demand can be admitted.
%If it is between $\beta_j^{k}$ and $\beta_j^{k+1}$, then the profit is $\alpha_j^k$, where $1>\alpha_j^1>\alpha_j^2>...>\alpha_j^k$.
%Otherwise, it is rejected, which means the network can't support $d$.
%where $R_j=\sum_{t \in T_j}f_{jt}/d_j$ and $f_{jtab}$.
%\sum_{\forall a,b \in V: t\in T_{ab}}f_{jtab}/d_{jab} 
%$\mu(f_{jtk}) $ aims to ensure that service $j$  will gain as much bandwidth as possible if the network fails to support the availability of service $j$.
which can further written as
\iffalse
\begin{equation}
\begin{cases}
S_d <  \beta_{d}\times  (1-y_d)+y_d,& \forall d \in D. \\
S_d \ge  \beta_{d} \times y_d,& \forall d \in D. \\
y_d\in\{0,1\},& \forall d \in D. \\
\end{cases}
\label{g-2}
\end{equation}
\fi
\begin{equation}
\label{g-2}
\begin{array}{rll}
a_d\in & \!\!\{0,1\},& \forall d \in D
s_d < & \!\!\beta_{d}\times  (1-a_d)+a_d,& \forall d \in D \\
s_d \ge & \!\!\beta_{d} \times a_d,& \forall d \in D \\
\end{array}
\end{equation}

>>>>

\begin{abstract}
Inter-DataCenter Wide Area Network (Inter-DC WAN) that connects geographically distributed data centers is becoming one of the most critical network infrastructures.
%Network failures are common in WANs, so the provision of high availability has been a major focus of network research.
Due to the limited bandwidth resources and inevitable link failures, it is highly challenging to guarantee network availability for services, especially those with stringent bandwidth demands, over inter-DC WAN.
%While modern datacenter services increasingly call for high availability, network failures in WANs remain a fairly common phenomenon.
%Most traffic engineering schemes only consider connectivity-based availability and this severely degrades quality of service, thus revenue.
We present $\mathsf{BATE}$,
a novel Traffic Engineering (TE)  framework that 
%contains admission control, online scheduling and failure recovery.
aims for \textit{bandwidth availability} (BA) provision, where a service level agreement (SLA) defines that a demand on certain bandwidth should be satisfied with a stipulated probability,  when subjected to the network capacity and possible failures of the inter-DC WAN.
%Also, $\mathsf{BATE}$ is able to maximize revenue when network fails.
%$\mathsf{BATE}$ tries to guarantee the bandwidth-based availability of demands . 
%$\mathsf{BATE}$ generates a probabilistic failure model from empirical data and maximizes the profit that can be achieved under certain constrains on  bandwidth-based availability. 
%For the failure model, we propose a pruning algorithm to reduce the problem size.
%For the optimization problem, we prove it is NP-hard and  propose a greedy algorithm to efficiently solve it with only minor profit loss. 
%We design and implement an SDN-based system named $\mathsf{Dionysus}$ to deploy $\mathsf{BATE}$ over inter-DC WAN.
The three core components of  $\mathsf{BATE}$, i.e., admission control, traffic scheduling and failure recovery, are built on different mathematical models and theoretically analyzed. 
They are also extensively compared against state-of-the-art TE schemes, using testbed as well as trace driven simulations across different topologies, traffic matrices and failure scenarios. 
Our evaluations on real network topologies and traces show that, compared with the optimal admission strategy, $\mathsf{BATE}$ can speed up the online admission control by 30$\times$ at the expense of less than 4\% false rejections. 
On the other hand, compared with the latest TE schemes like FFC and TEAVAR, $\mathsf{BATE}$ can meet the bandwidth availability SLAs for 23\%$\sim$60\% more demands under normal loads, and when network failure causes SLA violations, it can retain 10\%$\sim$20\% more profit under a simple pricing and refunding model.
%.
% $\mathsf{BATE}$ can 
%(1) achieve 30 $\times$ speedup in admission control time at the expense of sacrificing 8\% in performance compared to the optimal stragety;
%(2) increase the percentage of demands that satisfy their availability SLAs by up to 40\%;
%(3) hold 30\% more profit for the provider when network fails. 
%The evaluation results demonstrate that $\mathsf{BATE}$ can make 20\%, 25\%, 30\%, 40\% more flows satisfy their bandwidth-based availability demands  than TEAVAR, SMORE, SWAN and FFC, respectively.
\end{abstract}

@@

Thirdly, 
we implement $\mathsf{BATE}$ as a real system, including a centralized controller and multiple brokers (one for each DC),  together with end-host clients (see $\S$\ref{system}).
 We conduct extensive experiments using a small testbed as well as trace driven large scale simulations (see $\S$\ref{evaluation}).
We compare  $\mathsf{BATE}$ with state-of-the-art WAN TE schemes such as TEAVAR \cite{Teavar}, SMORE \cite{SMORE}, SWAN \cite{swan}, B4 \cite{B4} and FFC \cite{FFC}, across different topologies, traffic matrices and failure scenarios.
Our evaluations on real network topologies and traces demonstrate that, $\mathsf{BATE}$ can 
(1) speed up the online admission control by 30$\times $ at the expense of a false rejection ratio that is less than 4\%;
(2) meet the bandwidth availability SLAs for 23\%$\sim$60\% more demands under normal loads;
(3) retain 10\%$\sim$20\% more profit when network failure causes SLA violations, under a simple pricing and refunding model. 
To our knowledge, $\mathsf{BATE}$ is the first to tackle bandwidth availability provision over inter-DC WAN, where heterogeneities of demands and link failures are systematically taken into account for profit maximization.  
 %At last, we show the related works (see $\S$\ref{relate}).
%Traditionally, links are heavily underutilized to achieve a more rigorous availability target. 
%However, in reality, the failure probability of a single link can even differ by three orders of magnitude.
%Therefore, some link failure can be negligible and it makes no sense to reduce the utilization of these links.
%With the link Under BATE, links can maintain high utilization.

@@

If for every $k$, $R_{dk}$ is larger than its demand (i.e., $R_{dk} \ge 1$), 
then there is no problem since the demanded availability is still satisfied. 
However, if any $R_{dk}$ falls below 1, then the corresponding SLA will be violated. 
For simplicity, here we assume a simple pricing and refunding model, 
where the charge for serving a user demand $d$ is $g_d$, and if the SLA is violated, 
a fraction $\mu_d$ of $g_d$ will be refunded\footnote{There are also more complicated multi-stage SLAs, 
where $\mu_d$ can even be set to 1 under low availability. Our preliminary results show $\mathsf{BATE}$ will perform even better than the others under such more complicated SLAs.}. 
We use $r_d$ to denote the profit of demand $d$ with refunding, such that
%If it is between $\beta_j^{k}$ and $\beta_j^{k+1}$, then the profit is $\alpha_j^k$, where $1>\alpha_j^1>\alpha_j^2>...>\alpha_j^k$.
\begin{equation*}
r_d=
\begin{cases}
g_d &\text{if $R_{dk} \ge 1$ for every $k \in K$}\\
(1-\mu_{d})g_d &\text{Otherwise}
\end{cases}
\label{availability222}
\end{equation*}

@@

%We begin by describing the experimental framework ($\S$ \ref{setting}). 
%We show the performance of $\mathsf{BATE}$ through answering the following specific questions:
%compared with the latest TE schemes like FFC and TEAVAR, BATE can meet the availability SLAs of 40% more bandwidth demands, and when network failure causes SLA violations, it can retain 30% more profit under a simple pricing and refunding model.
(1) $\mathsf{BATE}$ consistently outperforms latests TE algorithms under various topologies, traffic matrices and failure scenarios. With $\mathsf{BATE}$, 23\%$\sim$60\% more BA demands can be successfully fulfilled under normal loads, and 10\%$\sim$20\% more profit can be retained when failures occur.

(2) $\mathsf{BATE}$ achieves a good tradeoff between efficiency and optimality. 
Compared with the optimal solutions, (i) our admission control algorithm can speed up the admission procedure by 30$\times$ at the expense of less than 4\% false rejections, 
(ii) our pruning-augmented scheduling algorithm runs $10^2 \sim 10^4 \times$ faster while wasting only 6\% total bandwidth, 
and (iii) our greedy failure recovery algorithm can reduce the reaction time by xx$\times$, 
where the profit loss is only around 10\%.

@@

\subsection{Simulations}
\textbf{Simulation setup.} 
We also conduct simulations on four real network topologies, including B4 \cite{B4}, ATT \cite{Teavar}, IBM\cite{SMORE} and a national-level backbone. 
Table \ref{evaluation-topologies} shows the topology details
\footnote{For B4, ATT and IBM, we get their topologies, link capacities and traffic matrices from the authors of TEAVAR\cite{Teavar}, and for the national backbone, we conduct a direct measurement on it but hide its name due to anonymity requirement.}. 
Following the conclusion on WAN failures in literature studies\cite{Characterization, Teavar}, 
we simulate link failures according to a Weibull distribution with its shape $\lambda=0.8$ and scale $k=0.00001$. 
We generate the demand workload in a similar way to that in the testbed. 
The arrivals of BA demands follow a Poisson process, where the mean arrival rate varies from 1 to 5 in each time slot. 
The duration of each demand follows an exponential distribution, and the mean duration corresponds to 1000 time slots.
The required bandwidth in each user demand is randomly drawn from the traffic metrices (we have collected 200 matrices for each topology) with a proper scale down factor\footnote{We use a factor of 5, and a mean arrival rate of 5 in our simulation corresponds to the normal network load.}, so that between each source-destination pair, multiple users can be served simultaneously. 
The required availability in each user demand is drawn from 10 different SLAs of Azure\cite{azure}.
In our simulations, besides FFC and TEAVAR, we also compare against several other TE algorithms,  
including SWAN \cite{swan}, SMORE \cite{SMORE} and B4 \cite{B4}. 
They have not explicitly considered availability, but pay attention to 
total throughput, link utilization or user fairness. 
These TE algorithms will be activated every 10 time slots.
We assume at most one link failure (i.e., no concurrent failures) in FFC,  
use 99.9\% (which is the maximum value in the user demands) as the default availability target in TEAVAR,
and let SWAN maximize the total throughput of all users. 
With the above settings, each simulation lasts 150,000 slots (corresponding to 100 days if each slot represents 1 minute), and the results achieved by each algorithm on each topology are calculated on 5 independent simulations with different workload traces. 
All the simulations are conducted on a Linux server with a quad-core 2.60GHz processor and 32GB memory.

@@

We then compare the traffic scheduling capability of $\mathsf{BATE}$ against FFC, TEAVAR, SWAN, SMORE and B4.
The methodology is similar to the post-processing simulation in TEAVAR \cite{Teavar}, 
where we simulate different failure scenarios according to their probabilities, 
and in each scenario we record the demands that can be satisfied. 
If the \textit{achieved availibility}, i.e., the total posterior probabilities of \textit{qualified} scenarios where a user's bandwidth target is met, is larger than the user's availability target, 
then the BA demand is \textit{satisfied}. 
We plot the overall percentage of satisfied BA demands under each arrival rate (averaged across all simulations) in Figure \ref{scheduling-benefit}(a). $\mathsf{BATE}$ nearly always achieves a satisfaction ratio around 100\%, with a leading margin of at least 23\% (with respect to TEAVAR) under a high arrival rate (rate=6 in the figure)\footnote{$\mathsf{BATE}$ leads FFC by around 60\%, which is not shown in the figure.}. 
To further demonstrates $\mathsf{BATE}$'s advantage in matching stringent availability requirements  
with reliable links, we further augment each TE algorithm with the \textit{fixed} admission control 
scheme. The satisfaction ratios are plotted in Figure \ref{scheduling-benefit}(b), where $\mathsf{BATE}$
still performs at least 10\% better than the others.

@@

Figure \ref{sim-profit} shows the average profit after failures occur in the network.
Due to its considration of pricing and refunding,  
$\mathsf{BATE}$ is able to retain 10\%$\sim$20\% more profit than the other algorithms.
\footnote{Our preliminary results show $\mathsf{BATE}$ will perform even better than the others under more complicated multi-stage SLAs, especially when the refunding ratio $\mu=1$ under low satisfaction.}

Remeber that our scaling down factor is 5, so these summarized results are all collected under normal network load, where the mean arrival rate in each slot is between 1 and 6. 
We note that, under heavier loads, $\mathsf{BATE}$ performs even better than its competitors, 
but we regard that as less possible in reality.

\begin{figure}
\centering
\subfigure[Bandwidth loss in pruning]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/error.pdf}}
\subfigure[Computation time]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/optimization_time.pdf}}
\caption{Impact of pruning on traffic scheduling}
\label{availability_fig3}
\end{figure}

@@

\begin{figure}[t]
   \begin{minipage}[t]{0.5\linewidth} 
    \centering 
    \includegraphics[width=1.6 in]{fig/evaluation/routing.pdf}
    \caption{Routing} 
    \label{routing-version} 
  \end{minipage}% 
   \begin{minipage}[t]{0.5\linewidth} 
    \centering 
    \includegraphics[width=1.6 in]{fig/evaluation/approximation.pdf}
    \caption{Approx ratio} 
    \label{approximation} 
  \end{minipage}

@@

\textbf{Optimality and Robustness.}
In traffic scheduling, $\mathsf{BATE}$ prune scenarios that are unlikely to happen.
%Algorithm \ref{pruning} runs in depth-first manner and when the current network state is smaller than the threshold, the remaining state of the search tree can be ignored.
%Figure \ref{purning_fig2} (a) shows the percentage of network state coverage.
%We can see that even with small cutoff threshold, more than 97\% probability are included.
% In Section \ref{solutions}, we show how to derive the solutions for WAPM problem.
% The errors mainly comes from two parts, i.e., ILP approximate algorithm and pruning.
%In Appendix \ref{B}, we analyze the approximation of the greedy heuristic is 2 in an ideal case.
%Algorithm \ref{greedy} proposes a greedy algorithm to solve $\mathsf{BATE}$ problem.
We compare the bandwidth allocated by $\mathsf{BATE}$ with that allocated by the optimal stragety, i.e., not pruning any scenarios. 
We calculate the bandwidth loss ratio, as well as the running time of $\mathsf{BATE}$, due to such an optimization, under each topology.
%Let $\mathsf{BATE}$ denote the overall allocated bandwidth of all admitted demands with scenario pruning  and $OPT$ denote the allocated bandwidth of optimal solution without scenario pruning. 
%Then the error can be defined as $\frac{|\mathsf{BATE} -OPT|}{|OPT|}$.
Figure \ref{availability_fig3}(a) plots the relative bandwidth loss ratio,  
where the highest number of concurrent link failures varies from 1 to 4. 
This indicates to what extend $\mathsf{BATE}$ will trade accuracy for efficiency. 
We can see the loss ratio is less than 8\% even when no current link failures are considered.
%Traditionally, TE should update the network state every 5-10 minutes.
% and though the powerful mathematical optimization solver such as Gurobi \cite{gurobi} can solve $\mathsf{BATE}$ problem, it might be too slow.
The corresponding computation time is plotted in Figure \ref{availability_fig3}(b), 
where we use Gurobi \cite{gurobi} to solve the pruned LP problem. 
%on the server (4-core, 2.60GHz processor with 32GB ).
We can see that even on a large network (e.g., ATT), 
at most 15 seconds are needed when we consider at most 2 current failures.
%We can see that for large network (e.g., ATT topology) , Gurobi is too slow to converge and the greedy algorithm is necessary.
%While the bruce force algorithm is more than 1000 minutes for each topology and we don't paint them in the picture.
%We can see the result is fast enough to deploy in practice.

By default, we use the K-shortest paths in the network as tunnels for transmission. 
To test the robustness of $\mathsf{BATE}$'s scheduling algorithm,
we further replace K-shortest path routing with oblivious routing\cite{SMORE} and  
edge disjoint path routing\cite{Bruno2013Dynamic}, which have been used by other TE algorithms.  
The BA demand satisfaction ratios are plotted in Figure \ref{routing-version}, 
where there are only minor difference between different tunnel selection algorithms.
Scheduling based on oblivious routing works slightly better than the other two, 
because it finds diverse and low-stretch paths and avoids link over-utilization.

Finally, we compute the approximation ratio of our greedy failure recovery algorithm, 
which is defined as dividing the optimal profit by the profit achieved. 
Figure \ref{approximation} shows that, 
our 2-approximation algorithm achieves a ratio between 1 and 1.25 in real scenarios, 
and the average profit loss is around 10\%.
%Satisfaction percentage. It denotes the percentages of applications whose achieved availability is larger than the corresponding target.
%Figure \ref{availability_fig1}(b) shows 
%$\mathsf{BATE}$ performs about 20\%, 25\%, 30\%,  40\% better than TEAVAR, SMORE, SWAN, FFC, respectively.
%%Specially, when traffic scale is 3, more than 70\% applications can satisfy their availability demands, which is at least 30\% better than TEAVAR.
%Specially, the advantage of $\mathsf{BATE}$  is more obvious when there are resource competition (e.g., $s=3$).
%%The reason for this is that $\mathsf{BATE}$ considers the bandwidth-based availability demand differentiation of applications.
%This picture also demonstrates that the performance of $\mathsf{BATE}$ doesn't depend on particular network topology and traffic.
%Next, we take IBM trace as the example and perform the experiments.

@@

Use $a_d$ to represent whether the BA target of $d$ can be satisfied, which also means $a_d$ can be admitted, then we have 
\iffalse
\begin{equation}
 y_d=
\begin{cases}
1 &\text{$1 >S_d \ge \beta_{d}$}\\
0 &\text{$ \beta_{d} >S_d\ge 0 $}
\end{cases},
\ \ \ \forall  d \in D.
\label{availability4}
\end{equation}
\fi
\begin{equation*}
a_d=
\begin{cases}
1 &\text{if $ \beta_{d} \le s_d \le 1$}\\
0 &\text{if $ 0 \le s_d< \beta_{d} $}
\end{cases}
\label{availability4}
\end{equation*}
%If the achieved bandwidth  availability (i.e., $s_d$) is larger than its desired availability target (i.e., $\beta_d$), the demand can be admitted.
%If it is between $\beta_j^{k}$ and $\beta_j^{k+1}$, then the profit is $\alpha_j^k$, where $1>\alpha_j^1>\alpha_j^2>...>\alpha_j^k$.
%Otherwise, it is rejected, which means the network can't support $d$.
%where $R_j=\sum_{t \in T_j}f_{jt}/d_j$ and $f_{jtab}$.
%\sum_{\forall a,b \in V: t\in T_{ab}}f_{jtab}/d_{jab} 
%$\mu(f_{jtk}) $ aims to ensure that service $j$  will gain as much bandwidth as possible if the network fails to support the availability of service $j$.
which can further written as
\iffalse
\begin{equation}
\begin{cases}
S_d <  \beta_{d}\times  (1-y_d)+y_d,& \forall d \in D. \\
S_d \ge  \beta_{d} \times y_d,& \forall d \in D. \\
y_d\in\{0,1\},& \forall d \in D. \\
\end{cases}
\label{g-2}
\end{equation}
\fi

\begin{equation}
\label{g-2}
\begin{array}{rll}
a_d\in & \!\!\{0,1\},& \forall d \in D \\
s_d < & \!\!\beta_{d}\times  (1-a_d)+a_d,& \forall d \in D \\
s_d \ge & \!\!\beta_{d} \times a_d,& \forall d \in D \\
\end{array}
\end{equation}
